Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-11-21 paper/main.tex
extend description of visualization

A render of this result can be seen in figure~\ref{fig:progression-image-generation}.
Since we use a 3D rendering engine for our visualization, the resulting image can have
overlaps of bacteria which are placed at higher or lower values along the z-direction.
To generate masks, we assign unique colours to every mesh of the respective cellular agent, ensuring
no two agents will use identical colours. \textbf{TODO semantic segmentation Citation}
We then use a parallel projection and remove any existing light sources in order to obtain a solid
color for every cell-agent.
The resulting image is shown in subfigure (B).

>>>>

A render of this result can be seen in figure~\ref{fig:progression-image-generation}.
Since we use a 3D rendering engine for our visualization, the resulting image can display
overlaps of bacteria which are placed at higher or lower values along the z-direction.
To generate masks, we use a pixel-based (in-image) encoding scheme~\cite{JianboShi2000}, thus
assigning unique colours to every mesh of the respective cellular agent, ensuring no two agents
will use identical colours.
We then use a parallel projection and remove any existing light sources in order to obtain a solid
color for every cell-agent.
The resulting image is shown in subfigure (B).
